---
title: "-body/-one variation"
author: "Justin Lo"
date: "13 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

These data were lifted from the D'Arcy et al (2013) paper: Assymetrical trajectories: The past and present of *-body/-one*. Data from 1570 onwards were visually esimated from Figure 4. Percentages prior to that were based on binary presence/absence of the form in Figure 1.

```{r}
quantifiers <- read.csv("body_one_variation.csv", stringsAsFactors = TRUE)
```

## Basic graph

This is a sample of the distribution of *-body* vs *-one* between 1750 and 1800. I chose a stacked bar chart because there is only one dimension (%) changing against time.

```{r slice, message = FALSE}
library(ggplot2)
library(dplyr)

var1750 <- quantifiers %>% filter(year == 1750)

ggplot(var1750, aes(x = quantifier, y = percentage)) +
  geom_bar(aes(fill = compound), stat = "identity")
```

## Animated graph

The idea is to show how the distribution of *-body* vs *-one* varies in throughout the course of history. To do this, we use the package `gganimate`, which extends the functionality of `ggplot2` to allow animation. The size of each bar transitions to achieve the visual effect. Obviously, the Middle English data are a bit wild, due to lack of actual data (and no comparison with the *-man* form).

```{r animate, message = FALSE}
library(gganimate)

ggplot(quantifiers, aes(x = quantifier, y = percentage)) +
  geom_bar(aes(fill = compound), stat = "identity") +
  # The following is what allows animation
  transition_states(
    year,
    transition_length = 2,
    state_length = 3
  ) +
  labs(title = "Year: {closest_state}")
```

Alternatively:

```{r animate-alt}
ggplot(quantifiers, aes(x = quantifier, y = percentage)) +
  geom_bar(aes(fill = compound), stat = "identity") +
  # The following is what allows animation
  transition_time(year) +
  ease_aes("sine-in-out") +
  labs(title = "Year: {frame_time}")
```